Online Social Cohesion Reflects Real-World Group Action in Syria during the Arab Spring

### 2020-06-05 manuscript-chicago.Rmd
More snipping

## Social Media and Social Movements

Massive online social cohesion can manifest in real-world social behavior.
Social media platforms enable online social cohesion by offering distributed
information-gathering and real-time information dissemination. Given its
accessibility and proficiency as an information exchange tool, Twitter has
provided social and political activists an opportunity to complement or even
replace real-world social mobilization. For example, during the 2012 Italian
protests for global economic change, the riots in Rome were mirrored by Twitter
activity both on the day of the protests and in the days following them
[@vicari2013public]. Tweeting was determined to be more effective locally in
discussing real-world, real-time events than traditional mainstream media
platforms. As people increasingly rely on social media for local news and
information, we must understand exactly how these micro-blogs connect to and
reflect real-world action. Some argue that these mass movements would not have
been possible without efficient large-scale coordination, both physically on the
ground and virtually on social media platforms.

@@

For social cohesion and count of positive events, we saw a downward trend in RR
as the window advances throughout the sample. Interestingly, we see largely
above-chance RR until the 50th window, with some exceptions during window
periods 19-30. DET was at or above chance for the 8th--17th, 32nd--33rd, and
60th windows (Figure \@ref(fig:plot-wcrqa-targ-all)).

For social cohesion and count of negative events, RR stayed above or almost
above chance from the 4th--7th and 43rd-47th windows. DET was above or nearly
above chance in the 1st and 2nd windows, with intermittent peaks in later
windows (Figure \@ref(fig:plot-wcrqa-targ-all)).

@@

For social cohesion and count of all events, there was a consistent period of
above- or nearly above-chance DET from the 7th--13th and 26th--47th windows. DET
also showed above- or nearly above-chance values in windows 7 through 17 and
intermittent peaks between the 34th and 61st windows (Figure
\@ref(fig:plot-wcrqa-source-targ-all)).

For social cohesion and count of positive events, there was a downward trend in
RR as the window moved, with largely above-chance values in the first 20 windows
and the 32nd--45th windows. DET stayed largely within chance, with the exception
of windows 13 through 19 (Figure \@ref(fig:plot-wcrqa-source-targ-all)).

@@

# Discussion
In the present study, we investigated the dynamics of real-world events and
online communication on Twitter in Syria during Arab Spring. CRQA methodology
allows us to disentangle the relationship between sociolinguistic cohesion and
exogenous political events. This work stands alongside the model of
Palestinian-Israeli social media and events developed by @zeitzoff2017social, and
the role of peripheral participants in the Syrian Arab Spring movement by
@steinert2017spontaneous. By introducing the CRQA and WCRQA methods, we
demonstrate how language and social mobilization interact with events along the
conflict-cooperation continuum in Syria. We have introduced a novel theoretical
framework of sociolinguistic cohesion which we operationalize using a weighted
measure of lexical relationships. We examined how virtual and physical social
mobilization evolve over time in tandem. Using nonlinear dynamical time series
analyses, we investigated the theory that virtual mobilization is increasingly
reflective of real-world events during times of strife.

>>>>

## Social Media and Social Movements
Massive online social cohesion can manifest in real-world social behavior.
Social media platforms enable online social cohesion by offering distributed
information-gathering and real-time information dissemination. Given its
accessibility and proficiency as an information exchange tool, Twitter has
provided social and political activists an opportunity to complement or even
replace real-world social mobilization. During the 2012 Italian protests for
global economic change, tweeting was determined to be more effective locally in
discussing real-world, real-time events than traditional mainstream media
platforms [@vicari2013public]. As people increasingly rely on social media for
local news and information, we must understand exactly how these micro-blogs
connect to and reflect real-world action.

@@

For social cohesion and count of positive events, we saw a downward trend in RR
as the window advances throughout the sample. Interestingly, we see largely
above-chance RR until the 50th window, with some exceptions during window
periods 19--30. DET was at or above chance for the 8th--17th, 32nd--33rd, and
60th windows (Figure \@ref(fig:plot-wcrqa-targ-all)).

For social cohesion and count of negative events, RR stayed above or almost
above chance from the 4th--7th and 43rd--47th windows. DET was above or nearly
above chance in the 1st and 2nd windows, with intermittent peaks in later
windows (Figure \@ref(fig:plot-wcrqa-targ-all)).

@@

For social cohesion and count of all events, there was a consistent period of
above- or nearly above-chance DET from the 7th--13th and 26th--47th windows. DET
also showed above- or nearly above-chance values in windows 7--17 and
intermittent peaks between the 34th and 61st windows (Figure
\@ref(fig:plot-wcrqa-source-targ-all)).

For social cohesion and count of positive events, there was a downward trend in
RR as the window moved, with largely above-chance values in the first 20 windows
and the 32nd--45th windows. DET stayed largely within chance, with the exception
of windows 13--19 (Figure \@ref(fig:plot-wcrqa-source-targ-all)).

@@

# Discussion
In the present study, we investigated the dynamics of real-world events and
online communication on Twitter in Syria during Arab Spring. CRQA methodology
allows us to disentangle the relationship between sociolinguistic cohesion and
exogenous political events. This work stands alongside the model of
Palestinian-Israeli social media and events developed by @zeitzoff2017social, and
the role of peripheral participants in the Syrian Arab Spring movement by
@steinert2017spontaneous. By introducing the CRQA and WCRQA methods, we
demonstrate how language and social mobilization interact with events along the
conflict-cooperation continuum in Syria. We have introduced a novel theoretical
framework of sociolinguistic cohesion which we operationalize using a weighted
measure of lexical relationships. Using nonlinear dynamical time series
analyses, we investigated the theory that virtual mobilization is increasingly
reflective of real-world events during times of strife.
